metric analysis

### 2021-10-29 metric_analysis.Rmd
Minor revisions from JGR

met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(year, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total winnd", 
         variable = "grd") -> 
  wind_df

>>>>

met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(year, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total wind", 
         variable = "grd") -> 
  wind_df
